Weighted Visibly Pushdown Automata and Automated Music Transcription

### 2021-04-29 main.tex
representations score, performances

\def\SWT{\textsf{SWT}\xspace}
\def\SWA{\textsf{SWA}\xspace}
\def\SWVPA{\textsf{SWVPA}\xspace}
\def\weight{\mathsf{weight}}
\def\wei{\mathsf{w}}
\def\init{\mathsf{in}}
\def\final{\mathsf{out}}
\newcommand{\call}[1]{\ensuremath \langle_{#1}}
\newcommand{\return}[1]{\ensuremath {}_{#1}{\rangle}} % $\prescript{}{a}{)}$
\def\Sigmai{{\Sigma_\mathsf{i}}}
\def\Sigmac{{\Sigma_\mathsf{c}}}
\def\Sigmar{{\Sigma_\mathsf{r}}}
\def\Phii{{\Phi_\mathsf{i}}}
\def\Phic{{\Phi_\mathsf{c}}}
\def\Phir{{\Phi_\mathsf{r}}}
\def\Phicr{{\Phi_\mathsf{cr}}}
\def\weii{{\wei_\mathsf{i}}}
\def\weic{{\wei_\mathsf{c}}}
\def\weir{{\wei_\mathsf{r}}}
\def\weie{{\wei_\mathsf{e}}}
\newcommand{\config}[2]{\ensuremath \genfrac{[}{]}{0pt}{}{#1}{#2}}

@@

\section{SW Visibly Pushdown Automata}
The following model generalizes Symbolic VPA~\cite{DAntonyAlur14SVPDA}
from Boolean semirings to arbitrary semiring weight domains.

@@

\section{Application}
Symbolic Automated Music Transcription

\subsection{Representations}

\paragraph{Performance.}

\paragraph{Score.}

\subsection{Transducer for Distance Computation}

>>>>

\def\SWT{\textsf{SWT}\xspace}
\def\SWA{\textsf{SWA}\xspace}
\def\SWVPA{\textsf{SWVPA}\xspace}
\def\weight{\mathsf{weight}}
\def\wei{\mathsf{w}}
\def\init{\mathsf{in}}
\def\final{\mathsf{out}}
\newcommand{\call}[1]{\ensuremath \langle_{#1}}
\newcommand{\return}[1]{\ensuremath {}_{#1}{\rangle}} % $\prescript{}{a}{)}$
\def\Sigmai{{\Sigma_\mathsf{i}}}
\def\Sigmac{{\Sigma_\mathsf{c}}}
\def\Sigmar{{\Sigma_\mathsf{r}}}
\def\Deltai{{\Delta_\mathsf{i}}}
\def\Deltac{{\Delta_\mathsf{c}}}
\def\Deltar{{\Delta_\mathsf{r}}}
\def\Phii{{\Phi_\mathsf{i}}}
\def\Phic{{\Phi_\mathsf{c}}}
\def\Phir{{\Phi_\mathsf{r}}}
\def\Phicr{{\Phi_\mathsf{cr}}}
\def\weii{{\wei_\mathsf{i}}}
\def\weic{{\wei_\mathsf{c}}}
\def\weir{{\wei_\mathsf{r}}}
\def\weie{{\wei_\mathsf{e}}}
\newcommand{\config}[2]{\ensuremath \genfrac{[}{]}{0pt}{}{#1}{#2}}

@@

\section{SW Visibly Pushdown Automata}
\label{section:SWVPA}
The following model generalizes Symbolic VPA~\cite{DAntonyAlur14SVPDA}
from Boolean semirings to arbitrary semiring weight domains.

@@

\section{Application}
Symbolic Automated Music Transcription
and analysis of music performances

\subsection{Time Scales}
Real-Time Unit (RTU) = seconds

\noindent 
Musical-Time Unit (MTU) = number of measures

\noindent 
conversion via tempo value

\subsection{Representation of Music Performances}
A musical performance is represented symbolically as a finite sequence of timestamped events.
similar to piano roll representation~\cite{Muller15fundamentals} chap.1

\noindent
We consider an infinite alphabet $\Sigma$ of MIDI-like 
events made of:
\begin{itemize}
\item a timestamp in RTU\\ %(real or int = nb samples ?)
      or IOI in RTU
\item a pitch value in 0..127
\item ON | OFF flag
\item a velocity value in 0..127
\end{itemize}

\subsection{Representation of Music Scores}
we consider here the case of monodies for the sake of simplificity.

A music score ris epresented as a structured word
= sequence of quantified events + markups,
see nested words~\cite{AlurMadhusudan09nested}.

We consider an alphabet $\Delta$, every symbol of which is 
composed of a tag, in a finite set $\Xi$, 
and an IOI duration value.
Moreover, $\Delta$ is partitioned into 
$\Delta = \Deltai \uplus \Deltac \uplus \Deltar$, 
like in Section~\ref{section:SWVPA}.

\noindent
The elements of $\Deltai$ represent events:
% (infinite alphabet of internal symbols) made of:
whose tags are one of:
\begin{itemize}
\item continuation (0) : tie or dot
\item note, grace note (pitch) or chord (pitch+)
\item rest
\item ...
\end{itemize}

\noindent
The elements of $\Deltac$ and $\Deltar$ are 
markups for the representation of groups of events
(linearization of rhythm trees \cite{jacquemard:hal-01138642}...)
- parentheses for time divisions : tuplets, bars...
tag %labels: 
contain info such as tuple number, beaming policy...

\noindent
The date or duration of events, in MTU (rational), 
can be computed with the markups and tags (e.g. grace note has duration 0).

\noindent
There are simultaneous events, since grace notes has duration 0. They are ordered.

\noindent
Finite bound on the number of duration ratio. ?

\subsection{Performance/Score Distance Computation}
with a transducer
